---
title: "Telco Customer Churn Project: Summary Paper"
author: "Group7-Bug Tornado"
#date: "today"
date: "`r Sys.Date()`"
# this style requires installing rmdformats package 
output:  
    rmdformats::readthedown:
      toc_float: true
      toc_depth: 3
      number_sections: true
      code_folding: hide
      includes:
        before_body: header.html
---

```{r init, include=FALSE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
library(ggplot2)
library(ggpubr)
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "hide", message = F, echo = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```

# Chapter 1: Introudction of Company 
## Basic Information
Telco Systems is a company which have been working on design and development of high-performance network communications over 40 years. It is the global leader in telecommunications, providing excellent telecommunication service for customers. The service includes 5G internet, networking slicing, and more on. In our group, all of us have not tried to analyze such a company in telecommunication field. 

## Reason of Choosing Telco Systems
The reason of choosing this company is that Telco provides large amount of home phone service and internet service. These two stuffs are unavoidable in contemporary society. People get used to take mobile phones to go outside, and they adapt to such a life with internet. When people stay at home, they spend majority of times with interenet no matter working or playing. We can say that people cannot leave internet nowadays. Therefore, the company which is providing these services are pretty crucial. Telco is a good company, but it also has some drawbacks. Not all users satisfy with service, so we want to know in what place Telco can make an improvement. We care about how customers say about Telco, and what they dislike. We are here to help the company to find specific problems, to avoid unnecessary customers churn. Through analyzing the company, we wonder what factors Telco can improve to let customers have greater experiences of using. The best way to know the using experience is based on customers' survey. Therefore, we choose a dataset about customers survey. 

# Chapter 2: Description of Dataset
## About Dataset
The Telco customer churn data contains information about Telco that provided home phone and Internet services to 7043 customers in California at the end of 2017 Quarter 3. Data includes customers' basic information and it indicates which customers have left, stayed, or signed up for their service.  
Studying such data can help companies identify the characteristics of lost customers, identify potential, soon-to-be-lost customers and develop appropriate strategies to retain them.  
The dataset is WA_Fn-UseC_-Telco-Customer-Churn.csv.
Before analyzing this dataset, we did some research about what churn represents, and why it is important to avoid churn in business. Churn in this dataset represents lost customers. Some people will be curious about why the company should spend time on retaining current customers or decreasing lost customers. In fact, acquire a new customer is much harder than retaining an existing customer. Company can pay for fewer price to retain existing customers rather than spend large amount of money on advertisement, and it is a profound strategy to maintain good reputation. Therefore, it is crucial to figure out current problems, and then to fix it up. 

## Variables

```{r import, include=FALSE}
customer <- data.frame(read.csv("WA_Fn-UseC_-Telco-Customer-Churn.csv"))
str(customer)
#head(customer)
```

```{r asfactor, include=FALSE}
for(i in 2:21){
  # tenure, MonthlyCharges, TotalCharges
  if (!(i %in% c(6, 19, 20))){
    customer[,i] = factor(customer[,i])
  }
}
levels(customer$SeniorCitizen) <- c("No", "Yes") # no=1, yes=2
str(customer)
```

```{r cleanNA, include=FALSE}
summary(customer)  # there are 11 NA in TotalCharges
customer <- na.omit(customer)
sum(is.na(customer))
```

* `gender`: Female or Male
* `SeniorCitizen`: customer is a senior citizen or not (Yes, No)
* `Partner`: customer has a partner or not (Yes, No)
* `Dependents`: customer has dependents or not (Yes, No)
* `tenure`: number of months the customer has stayed with the company
* `PhoneService`: customer has a phone service or not (Yes, No)
* `MultipleLines`: customer has multiple lines or not (Yes, No, No phone service)
* `InternetService`: customer’s internet service provider (DSL, Fiber optic, No)
* `OnlineSecurity`: customer has online security or not (Yes, No, No internet service)
* `OnlineBackup`: customer has online backup or not (Yes, No, No internet service)
* `DeviceProtection`: customer has device protection or not (Yes, No, No internet service)
* `TechSupport`: customer has tech support or not (Yes, No, No internet service)
* `StreamingTV`: customer has streaming TV or not (Yes, No, No internet service)
* `StreamingMovies`: customer has streaming movies or not (Yes, No, No internet service)
* `Contract`: contract term of the customer (Month-to-month, One year, Two year)
* `PaperlessBilling`: customer has paperless billing or not (Yes, No)
* `PaymentMethod`: Electronic check, Mailed check, Bank transfer (automatic), Credit card (automatic)
* `MonthlyCharges`: amount charged monthly
* `TotalCharges`: total amount charged
* `Churn`: customer churned or not (Yes or No)

For our exploratory data analysis, we did some preprocessing including cleaning up and converting. We dropped “NA” values from the dataset to simplify our analysis; we convert `tenure`, `MonthlyCharges`, `TotalCharges` into factor variables. 

# Chapter 3: Categorical Variables EDA  

A brief overview of the dataset tells that there are 1869 customers left the telephone service company and 5163 who didn't. Below we'll call these left customers as churned customers.  

## Churn vs Not Churn
### What are churned customers look like?

```{r, include=FALSE}
churn <- subset(customer, Churn=="Yes")
stay <- subset(customer, Churn=="No")
summary(churn)
```
```{r, include=FALSE}
xkablesummary(subset(churn, select=c(SeniorCitizen, Partner, Dependents, PhoneService, InternetService, PaperlessBilling)), title="Churned Customer Attributes")
haveInt <- subset(churn, InternetService!="No")
xkablesummary(subset(haveInt, select=c(OnlineSecurity, OnlineBackup, DeviceProtection, TechSupport)))
xkablesummary(subset(churn, select=c(Contract, PaymentMethod)), title="Churned Customer Attributes2")
```
Here we have picked out a few factors from the summary that have a significant difference between factor levels.  `r xkablesummary(subset(churn, select=c(SeniorCitizen, Partner, Dependents, PhoneService, InternetService, PaperlessBilling)), title="Churned Customer Attributes")`
We see that most churned customers are `senior citizens`. Indeed, the age limit can cause them to leave. Also most churned customers have `no dependents`, which means they may be older and have their own considerations about choosing a phone company. From the table, we also see that most churned customers don't have a partner and have signed up for phone service and paperless billing. However, we cannot assume a direct reason at this time, so we'll talk about this later.  
Customers who signed up for an internet service with `Fiber Optic` quit most. This may be because that they are not satisfied with Fiber Optic, but this speculation must be based on the assumption that total numbers of customers with Fiber Optic and DSL are nearly equal. From the summary, there are 2416 customers with DSL and 3096 customers with Fiber Optic, therefore, the speculation holds.  

Then we want to take a deeper look into churned customers who have signed up for Internet Services.  `r xkablesummary(subset(haveInt, select=c(OnlineSecurity, OnlineBackup, DeviceProtection, TechSupport)), title="Attributes of Churned Customer with Internet Servies")`  
Here we see significant impacts with these four internet service add-on. Most churned customers didn't sign up for these four add-on.  

Now let's look at the `contract` and `payment method`.  
`r xkablesummary(subset(churn, select=c(Contract, PaymentMethod)), title="Churned Customer Attributes2")`
Most churned customers have short-term(month-to-month) contract and paid bills with electronic check.  

### Contrast Churned with not Churned  
Since the sample sizes of churned and not churned customers are different, we can't compare the numbers of customers directly for each attributes. Instead, we compare the percentage.  
Here we see the factors that have a significant impact on customer churn or not. Just as we mentioned earlier, these factors also characterize most churned customers.  
```{r, include=FALSE}
haveIntAll <- subset(customer, InternetService!="No")
```
```{r}
senior <- ggplot(customer, aes(x=SeniorCitizen, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("No" = "Not senior", "Yes" = "Senior")) +
                   labs(title="SeniorCitizen", x="", y="Percentage") +
                   theme(legend.position="top")
partner <- ggplot(customer, aes(x=Partner, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("No" = "Have no partner", "Yes" = "Have a partner")) +
                   labs(title="Partner", x="", y="Percentage") +
                   theme(legend.position="top")
dependent <- ggplot(customer, aes(x=Dependents, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("No" = "Have no dependents", "Yes" = "Have dependents")) +
                   labs(title="Dependent", x="", y="Percentage") +
                   theme(legend.position="top")
internet_service <- ggplot(customer, aes(x=InternetService, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Internet services", x="Internet company", y="Percentage") +
                   theme(legend.position="top")
online_security <- ggplot(haveIntAll, aes(x=OnlineSecurity, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Online security", x="", y="Percentage") +
                   theme(legend.position="top")
online_backup <- ggplot(haveIntAll, aes(x=OnlineBackup, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Online backup", x="", y="Percentage") +
                   theme(legend.position="top")
device_protection <- ggplot(haveIntAll, aes(x=DeviceProtection, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Device protection", x="", y="Percentage") +
                   theme(legend.position="top")
tech_support <- ggplot(haveIntAll, aes(x=TechSupport, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Tech support", x="", y="Percentage") +
                   theme(legend.position="top")
contract <- ggplot(customer, aes(x=Contract, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Contract", x="Method", y="Percentage") +
                   theme(legend.position="top")
paperless_billing <- ggplot(customer, aes(x=PaperlessBilling, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("No" = "No paperless billing", "Yes" = "Have paperless billing")) +
                   labs(title="Paperless billing", x="", y="Percentage") +
                   theme(legend.position="top")
payment_method <- ggplot(customer, aes(x=PaymentMethod, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("Bank transfer (automatic)" = "bank transfer", "Electronic check" = "E-check", "Credit card (automatic)" = "credit card")) +
                   labs(title="Payment method", x="Method", y="Percentage") +
                   theme(legend.position="top")
ggarrange(senior, partner, dependent, paperless_billing)
ggarrange(internet_service, online_security, online_backup, device_protection, tech_support)
ggarrange(contract, payment_method, nrow=2, ncol=1)
```
Remember we previously talked about the partner, phone service and paperless bill, which we are unsure why they have an impact on customer churn, they also create differences between churned and not churned customers. Let's find out whether these factors have significant impacts on churn with tests.  

## Chi-square Tests  
We use $\chi^2$ test to test if two categorical variables are independent base on contingency table.  

### Test Partner  

```{r}
churn_vs_partner = table(customer$Churn, customer$Partner)
```
Are they independent?  
- $H_0$: churn and partner are independent.  
- $H_1$: they are not independent. 
```{r, results='markup'}
chi_test1 = chisq.test(churn_vs_partner)
chi_test1
```
Since p-value = `r format(chi_test1$p.value, scientific=T)` < 0.05, we reject null hypothesis, so `partner` actually has a significant impact on churn.  

### Test PhoneService  

```{r}
churn_vs_phone = table(customer$Churn, customer$PhoneService)
churn_vs_phone
```
Are they independent?  
- $H_0$: churn and phone service are independent.  
- $H_1$: they are not independent. 
```{r, results='markup'}
chi_test2 = chisq.test(churn_vs_phone)
chi_test2
```
Since p-value = `r format(chi_test2$p.value, scientific=F)` > 0.05, we fail to reject null hypothesis, so `phone service` does not have a significant impact on churn.  

### Test PaperlessBilling  

```{r}
churn_vs_bill = table(customer$Churn, customer$PaperlessBilling)
churn_vs_bill
```
Are they independent?  
- $H_0$: churn and paperless bill are independent.  
- $H_1$: they are not independent. 
```{r, results='markup'}
chi_test3 = chisq.test(churn_vs_bill)
chi_test3
```
Since p-value = `r format(chi_test3$p.value, scientific=T)` < 0.05, we reject null hypothesis, and `paperless bill` service has a significant impact on churn.  