---
title: "Telco Customer Churn Project"
author: "Group7-Bug Tornado"
#date: "today"
date: "`r Sys.Date()`"
# this style requires installing rmdformats package 
output:  
    rmdformats::readthedown:
      toc_float: true
      toc_depth: 3
      number_sections: true
      code_folding: hide
      includes:
        before_body: header.html
---

```{r init, include=FALSE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
library(ggplot2)
library(ggpubr)
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```

# Description
The Telco customer churn data contains information about a telephone company that provided home phone and Internet services to 7043 customers in California at the end of 2017 Quarter 3. It indicates which customers have left, stayed, or signed up for their service.  
Studying such data can help companies identify the characteristics of lost customers, identify potential, soon-to-be-lost customers and develop appropriate strategies to retain them.  
The dataset is WA_Fn-UseC_-Telco-Customer-Churn.csv.  

## variables

* `gender`: Female or Male
* `SeniorCitizen`: customer is a senior citizen or not (Yes, No)
* `Partner`: customer has a partner or not (Yes, No)
* `Dependents`: customer has dependents or not (Yes, No)
* `tenure`: number of months the customer has stayed with the company
* `PhoneService`: customer has a phone service or not (Yes, No)
* `MultipleLines`: customer has multiple lines or not (Yes, No, No phone service)
* `InternetService`: customer’s internet service provider (DSL, Fiber optic, No)
* `OnlineSecurity`: customer has online security or not (Yes, No, No internet service)
* `OnlineBackup`: customer has online backup or not (Yes, No, No internet service)
* `DeviceProtection`: customer has device protection or not (Yes, No, No internet service)
* `TechSupport`: customer has tech support or not (Yes, No, No internet service)
* `StreamingTV`: customer has streaming TV or not (Yes, No, No internet service)
* `StreamingMovies`: customer has streaming movies or not (Yes, No, No internet service)
* `Contract`: contract term of the customer (Month-to-month, One year, Two year)
* `PaperlessBilling`: customer has paperless billing or not (Yes, No)
* `PaymentMethod`: Electronic check, Mailed check, Bank transfer (automatic), Credit card (automatic)
* `MonthlyCharges`: amount charged monthly
* `TotalCharges`: total amount charged
* `Churn`: customer churned or not (Yes or No)

```{r import, include=FALSE}
customer <- data.frame(read.csv("WA_Fn-UseC_-Telco-Customer-Churn.csv"))
str(customer)
#head(customer)
```

```{r asfactor, include=FALSE}
for(i in 2:21){
  # tenure, MonthlyCharges, TotalCharges
  if (!(i %in% c(6, 19, 20))){
    customer[,i] = factor(customer[,i])
  }
}
levels(customer$SeniorCitizen) <- c("No", "Yes") # no=1, yes=2
str(customer)
```

```{r cleanNA, include=FALSE}
summary(customer)  # there are 11 NA in TotalCharges
customer <- na.omit(customer)
sum(is.na(customer))
```

# Exploratory Data Analysis (EDA)
## Demographic information about customers
```{r basicInfo plot}
# gender seniorCitizen partner depedents
gender <- ggplot(customer, aes(x=gender, fill=Churn)) +
                  geom_bar(position="fill") +
                  scale_fill_manual(values=c("pink3", "steelblue")) +
                  labs(title="Gender", x="", y="Percentage") +
                  theme(legend.position="top")
senior <- ggplot(customer, aes(x=SeniorCitizen, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("No" = "Not senior", "Yes" = "Senior")) +
                   labs(title="SeniorCitizen", x="", y="Percentage") +
                   theme(legend.position="top")
partner <- ggplot(customer, aes(x=Partner, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("No" = "Have no partner", "Yes" = "Have a partner")) +
                   labs(title="Partner", x="", y="Percentage") +
                   theme(legend.position="top")
dependent <- ggplot(customer, aes(x=Dependents, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("No" = "Have no dependents", "Yes" = "Have dependents")) +
                   labs(title="Dependent", x="", y="Percentage") +
                   theme(legend.position="top")
basicInfo <- ggarrange(gender, senior, partner, dependent)
annotate_figure(basicInfo, top = text_grob("Customer Basic Infomation", 
               color = "Black", face = "bold", size = 14))
```
## Services customers has signed up for
```{r PhoneInfo plot}
# PhoneService MultipleLines
phone_service <- ggplot(customer, aes(x=PhoneService, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("No" = "Have no phone service", "Yes" = "have phone services")) +
                   labs(title="Phone Service", x="", y="Percentage") +
                   theme(legend.position="top")
multiple_lines <- ggplot(customer, aes(x=MultipleLines, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("No" = "Have no multiple lines", "Yes" = "Have multiple lines")) +
                   labs(title="Multiple lines", x="", y="Percentage") +
                   theme(legend.position="top")

PhoneInfo <- ggarrange(phone_service, multiple_lines)
annotate_figure(PhoneInfo, top = text_grob("Phone Infomation", 
               color = "Black", face = "bold", size = 14))
```

```{r InternetInfo plot }
#InternetService OnlineSecurity OnlineBackup DeviceProtection TechSupport StreamingTV StreamingMovies
internet_service <- ggplot(customer, aes(x=InternetService, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Internet services", x="Internet company", y="Percentage") +
                   theme(legend.position="top")
online_security <- ggplot(customer, aes(x=OnlineSecurity, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Online security", x="", y="Percentage") +
                   theme(legend.position="top")
online_backup <- ggplot(customer, aes(x=OnlineBackup, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Online backup", x="", y="Percentage") +
                   theme(legend.position="top")
device_protection <- ggplot(customer, aes(x=DeviceProtection, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Device protection", x="", y="Percentage") +
                   theme(legend.position="top")
tech_support <- ggplot(customer, aes(x=TechSupport, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Tech support", x="", y="Percentage") +
                   theme(legend.position="top")

InternetInfo <- ggarrange(internet_service, online_security, online_backup,                                                device_protection, tech_support)
annotate_figure(InternetInfo, top = text_grob("Internet Information", 
               color = "Black", face = "bold", size = 14))
```

```{r StreamingInfo plot}
#StreamingTV StreamingMovies
streaming_TV <- ggplot(customer, aes(x=StreamingTV, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Streaming tv", x="", y="Percentage") +
                   theme(legend.position="top")
streaming_movies <- ggplot(customer, aes(x=StreamingMovies, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Streaming movies", x="", y="Percentage") +
                   theme(legend.position="top")

StreamingInfo <- ggarrange(streaming_TV, streaming_movies)
annotate_figure(StreamingInfo, top = text_grob("Streaming Information", 
               color = "Black", face = "bold", size = 14))
```
## Customer account information
```{r PaymentInfo plot}
#Contract PaperlessBilling PaymentMethod
contract <- ggplot(customer, aes(x=Contract, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Contract", x="Method", y="Percentage") +
                   theme(legend.position="top")
paperless_billing <- ggplot(customer, aes(x=PaperlessBilling, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   scale_x_discrete(labels=c("No" = "No paperless billing", "Yes" = "Have paperless billing")) +
                   labs(title="Paperless billing", x="", y="Percentage") +
                   theme(legend.position="top")
payment_method <- ggplot(customer, aes(x=PaymentMethod, fill=Churn)) +
                   geom_bar(position="fill") +
                   scale_fill_manual(values=c("pink3", "steelblue")) +
                   labs(title="Payment method", x="Method", y="Percentage") +
                   theme(legend.position="top")

PaymentInfo <- ggarrange(contract, paperless_billing, payment_method)
annotate_figure(PaymentInfo, top = text_grob("Payment Information", 
               color = "Black", face = "bold", size = 14))
```

```{r kdePlot}
tenure <- ggplot(data = customer, aes(x = tenure, color = Churn)) + 
            geom_density(aes(fill = Churn), alpha = 0.8) + 
             scale_fill_manual(values=c("pink3", "steelblue")) +
              labs(title="KDEplot for tenure") +
               labs(x="tenure", y="density") +
                theme(legend.position="top")
tenure

MonthlyCharges <- ggplot(data = customer, aes(x = MonthlyCharges, color = Churn)) + 
                   geom_density(aes(fill = Churn), alpha = 0.8) + 
                    scale_fill_manual(values=c("pink3", "steelblue")) +
                     labs(title="KDEplot for MonthlyCharges") +
                      labs(x="MonthlyCharges", y="density") +
                       theme(legend.position="top")
MonthlyCharges

TotalCharges <- ggplot(data = customer, aes(x = TotalCharges, color = Churn)) + 
                   geom_density(aes(fill = Churn), alpha = 0.8) + 
                    scale_fill_manual(values=c("pink3", "steelblue")) +
                     labs(title="KDEplot for TotalCharges") +
                      labs(x="TotalCharges", y="density") +
                       theme(legend.position="top")
TotalCharges
```

```{r BoxPlot}
tenure_boxplot <- ggplot(customer, aes(x=Churn, y=tenure, fill=Churn)) + 
                   geom_boxplot( colour=c("pink3","steelblue"), outlier.size=2) +
                    labs(title="tenure vs Churn boxplot ", x="Churn", y = "tenure")
tenure_boxplot
MonthlyCharges_boxplot <- ggplot(customer, aes(x=Churn, y=MonthlyCharges, fill=Churn)) + 
                           geom_boxplot( colour=c("#ff0000","#11cc11"), outlier.size=2) +
                            labs(title="MonthlyCharges vs Churn boxplot ", x="Churn", y = "MonthlyCharges")
MonthlyCharges_boxplot
TotalCharges_boxplot <- ggplot(customer, aes(x=Churn, y=TotalCharges, fill=Churn)) + 
                         geom_boxplot( colour=c("pink3","steelblue"), outlier.size=2) +
                          labs(title="TotalCharges vs Churn boxplot ", x="Churn", y = "TotalCharges")
TotalCharges_boxplot
```

```{r LogisticRegression}
lm1 <- glm(Churn~tenure, family = binomial(link = "logit"), data = customer)
lm2 <- glm(Churn~tenure + MonthlyCharges, family = binomial(link = "logit"), data = customer)
lm3 <- glm(Churn~tenure + MonthlyCharges + TotalCharges, family = binomial(link = "logit"), data = customer)
anova(lm1,lm2,lm3, test="LRT")
```
Logistic regression is the appropriate regression analysis to predict a binary outcome (the dependent variable) based on a set of independent variables.


```{r AUClm2}
prob <- predict(lm2,customer, type = c("response"))
customer$prob <- prob
library(pROC)
g <- roc(Churn ~ prob, data = customer)
plot(g)
auc(customer$Churn, prob)
```

```{r AUClm}
prob1 <- predict(lm3,customer, type = c("response"))
customer$prob <- prob1
library(pROC)
g1 <- roc(Churn ~ prob1, data = customer)
plot(g1)
auc(customer$Churn, prob1)
```
AUC (Area Under The Curve) - ROC (Receiver Operating Characteristics) curve is a performance measurement for the classification problems at various threshold settings. ROC is a probability curve and AUC represents the degree or measure of separability. It tells how much the model is capable of distinguishing between classes. Higher the AUC, the better the model is at predicting 0 classes as 0 and 1 classes as 1. By analogy, the Higher the AUC, the better the model is at distinguishing between customer with churn and no churn.



```{r fitmodel}
summary(lm2)
```
As we can see from this summary, tenure has negative correlated with churn and monthlycharges has positive correlated with churn. It means when we have a customer with lower tenure and high monthlycharges having more probability to churn. 


## Simple correlations
Since most of variables are factors, it makes more sense to check their Spearman correlations.  
```{r correlationPlot, fig.dim=c(8, 8)}
customerNum = customer
# convert categorical variable as numeric for spearman method
for(i in 2:21){
  # tenure, MonthlyCharges, TotalCharges
  if (!(i %in% c(6, 19, 20))){
    customerNum[,i] = as.numeric(customerNum[,i])
  }
}
#str(customerNum)

# corrplot with spearman method for categorical variables
customercor <- cor(subset(customerNum, select=-c(customerID)), method="spearman")
#customercor
loadPkg("corrplot")
#corrplot.mixed(customercor, tl.pos = "lt", number.cex = .5, tl.cex=0.8)
corrplot(customercor, type="lower", addCoef.col="black", number.cex=0.5, tl.cex=0.7,title="Telco Customer Churn Correlation", mar=c(0,0,1,0))
unloadPkg("corrplot")
```

Larger circle means higher correlation. We can see that churn has negative correlation with contract and tenure, which means that customer who stays longer with the company or has a longer contract terms is less likely to churn. Customer who signed up for online security service and  has technical support plan is also less likely to churn. So it makes sense that contract and tech support have positive correlation, which means most customers who signed up for a technical support plan also have longer contract term.  