---
title: "KNN"
author: "Yuan Dang"
#date: "today"
date: "`r Sys.Date()`"
# this style requires installing rmdformats package 
output:  
    rmdformats::readthedown:
      toc_float: true
      toc_depth: 3
      number_sections: true
      code_folding: hide
      includes:
        before_body: header.html
---

```{r init, include=FALSE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
library(ggplot2)
library(ggpubr)
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```

# Telco Customer Churn
## Description
The Telco customer churn data contains information about a telephone company that provided home phone and Internet services to 7043 customers in California at the end of 2017 Quarter 3. It indicates which customers have left, stayed, or signed up for their service.  
Studying such data can help companies identify the characteristics of lost customers, identify potential, soon-to-be-lost customers and develop appropriate strategies to retain them.  
The dataset is WA_Fn-UseC_-Telco-Customer-Churn.csv.  

### variables

* `gender`: Female or Male
* `SeniorCitizen`: customer is a senior citizen or not (Yes, No)
* `Partner`: customer has a partner or not (Yes, No)
* `Dependents`: customer has dependents or not (Yes, No)
* `tenure`: number of months the customer has stayed with the company
* `PhoneService`: customer has a phone service or not (Yes, No)
* `MultipleLines`: customer has multiple lines or not (Yes, No, No phone service)
* `InternetService`: customer’s internet service provider (DSL, Fiber optic, No)
* `OnlineSecurity`: customer has online security or not (Yes, No, No internet service)
* `OnlineBackup`: customer has online backup or not (Yes, No, No internet service)
* `DeviceProtection`: customer has device protection or not (Yes, No, No internet service)
* `TechSupport`: customer has tech support or not (Yes, No, No internet service)
* `StreamingTV`: customer has streaming TV or not (Yes, No, No internet service)
* `StreamingMovies`: customer has streaming movies or not (Yes, No, No internet service)
* `Contract`: contract term of the customer (Month-to-month, One year, Two year)
* `PaperlessBilling`: customer has paperless billing or not (Yes, No)
* `PaymentMethod`: Electronic check, Mailed check, Bank transfer (automatic), Credit card (automatic)
* `MonthlyCharges`: amount charged monthly
* `TotalCharges`: total amount charged
* `Churn`: customer churned or not (Yes or No)

```{r import, include=FALSE}
customer <- data.frame(read.csv("WA_Fn-UseC_-Telco-Customer-Churn.csv"))
str(customer)
#head(customer)
```

```{r asfactor, include=FALSE}
for(i in 2:21){
  # tenure, MonthlyCharges, TotalCharges
  if (!(i %in% c(6, 19, 20))){
    customer[,i] = factor(customer[,i])
  }
}
levels(customer$SeniorCitizen) <- c("No", "Yes") # no=1, yes=2
str(customer)
```

```{r cleanNA}
summary(customer)  # there are 11 NA in TotalCharges
customer <- na.omit(customer)
sum(is.na(customer))
str(customer)
```
```{r}
#customer$customerID=NULL
#str(customer)
#xkablesummary(customer[1:7])
#xkablesummary(customer[8:14])
#xkablesummary(customer[15:20])
```
```{r Into Numeric}
customerNum = customer
# convert categorical variable as numeric 
for(i in 2:21){
  # tenure, MonthlyCharges, TotalCharges
  if (!(i %in% c(6, 19, 20))){
    customerNum[,i] = as.numeric(customerNum[,i])
  }
}
customerNum$customerID = NULL
str(customerNum)
```

```{r PCA}
customerx <- customerNum[1:19]
pra_scale =prcomp(customerx, scale =TRUE) # center=TRUE is the default
print(summary(pra_scale))
print(pra_scale$rotation)
```

```{r}
pca_var <- (pra_scale$sdev^2)
pve <- pca_var/sum(pca_var)
plot(cumsum(pve), xlab="Principal Component (standardized)", ylab ="Cumulative Proportion of Variance Explained",ylim=c(0,1),type="b")
```

```{r pcr_modeling}
loadPkg("pls")
customer_pc=PCAxform(customerx, z=TRUE )
customer_pc$Churn = customerNum$Churn
head(customer_pc)
```

```{r model1}
library(pscl)
pcModel = glm("Churn~.", data=customer_pc)
xkabledply(pcModel, title = "Full model using Principal Comps")
summary(pcModel)
pR2(pcModel)
xkablevif(pcModel)
```

```{r with significant}
customer_pc2 <- subset(customer_pc, select = -c(PC7,PC8,PC9,PC10,PC13,PC15,PC17))
pcModel2 = glm("Churn~.", data=customer_pc2)
xkabledply(pcModel2, title = "Model using Significant Principal Comps")
summary(pcModel2)
pR2(pcModel2)
xkablevif(pcModel2)
```

```{r with very significant}
customer_pc3 <- subset(customer_pc, select = -c(PC7,PC8,PC9,PC10,PC13,PC15,PC17,PC6,PC11,PC12,PC16))
#customer_pc3$Churn <- factor(customer_pc3)
#levels(customer_pc3$Churn) <- c(0,1)
pcModel3 = glm("Churn~.", data=customer_pc3)
xkabledply(pcModel3, title = "Model using Significant Principal Comps")
summary(pcModel3)
pR2(pcModel3)
xkablevif(pcModel3)
```

```{r}
set.seed(1)
customer_sampe <- sample(2, nrow(customerNum), replace=TRUE, prob=c(0.67, 0.33))
#str(customerNum)
train <- customerNum[customer_sampe==1, 1:20]
test <- customerNum[customer_sampe==2, 1:19]
# y
test_y <- customerNum[customer_sampe==2, 20]
pcModel4 <- pcr(Churn~. ,data=train,scale=TRUE,validation="CV")
summary(pcModel4)
validationplot(pcModel4,val.type="MSEP")
```
```{r}
au <- data.frame(test)
au$Churn = test_y
au$pcr_pred <- predict(pcModel4, test, ncomp = 14)
#df_predict <- data.frame(pc_pred,test_y)
library(pROC)
h <- roc(Churn~pcr_pred, data=au)
plot(h)
auc(h)
```

```{r preproccessing}
customer_final=customerNum
customer_final$Churn <-  factor(customer_final$Churn)
str(customer_final)
cusKNN <- subset(customer_final, select=c(SeniorCitizen, Partner, Dependents, PaperlessBilling, OnlineSecurity, OnlineBackup, DeviceProtection, TechSupport, Contract, tenure, MonthlyCharges, Churn))
str(cusKNN)
cus_scale = cusKNN
cus_scale[10:11]<- scale(cusKNN[10:11], center = TRUE, scale = TRUE)
cus_scale$Churn <- customer_final$Churn
str(cus_scale)
```
```{r train_test_split}
#customer_sampe <- sample(2, nrow(cusKNN), replace=TRUE, prob=c(0.67, 0.33))
#cus_train <- cusKNN[customer_sampe==1, 1:11]
#cus_test <- cusKNN[customer_sampe==2, 1:11]
# y
#cus_train_y <- cusKNN[customer_sampe==1, 12]
#cus_test_y <- cusKNN[customer_sampe==2, 12]
set.seed(1)
customer_sampe <- sample(2, nrow(cus_scale), replace=TRUE, prob=c(0.67, 0.33))
cus_train <- cus_scale[customer_sampe==1, 1:11]
cus_test <- cus_scale[customer_sampe==2, 1:11]
# y
cus_train_y <- cus_scale[customer_sampe==1, 12]
cus_test_y <- cus_scale[customer_sampe==2, 12]
```

```{r}
str(cus_train)
str(cus_test)
```
#```{r cutoff}
#library(ggplot2)
#library(ggthemes)

#cus_test$Churn = cus_test_y
#str(cus_test)
#ggplot(cus_test, aes(pred, color=Churn))+
#  geom_density(size=1) +
#  scale_color_economist(name="Churn", labels=c("No", "Yes")) +
#  theme_economist()
#```

```{r selectk}
loadPkg("class")
chooseK = function(k, train_set, val_set, train_class, val_class){
  
  # Build knn with k neighbors considered.
  set.seed(1)
  class_knn = knn(train = train_set,    #<- training set cases
                  test = val_set,       #<- test set cases
                  cl = train_class,     #<- category for classification
                  k = k) #,                #<- number of neighbors considered
                  # use.all = TRUE)       #<- control ties between class assignments. If true, all distances equal to the k-th largest are included
  
  tab = table(class_knn, val_class)
  
  # Calculate the accuracy.
  accu = sum(tab[row(tab) == col(tab)]) / sum(tab)                         
  cbind(k = k, accuracy = accu)
}

# The sapply() function plugs in several values into our chooseK function.
# function(x)[function] allows you to apply a series of numbers
# to a function without running a for() loop.
knn_different_k = sapply(seq(1, 21, by = 2),  #<- set k to be odd number from 1 to 21
                         function(x) chooseK(x, 
                                             train_set = cus_train,
                                             val_set = cus_test,
                                             train_class = cus_train_y,
                                             val_class = cus_test_y))

# Reformat the results to graph the results.
str(knn_different_k)
knn_different_k = data.frame(k = knn_different_k[1,],
                             accuracy = knn_different_k[2,])

# Plot accuracy vs. k.
# install.packages("ggplot2")
loadPkg("ggplot2")

ggplot(knn_different_k,
       aes(x = k, y = accuracy)) +
  geom_line(color = "orange", size = 1.5) +
  geom_point(size = 3) + 
  labs(title = "accuracy vs k")

```

```{r KNN}
pred <- knn(train = cus_train, test = cus_test, cl=cus_train_y, k=9)
pred
```
```{r}
loadPkg("caret") 
cm = confusionMatrix(pred, reference = cus_test_y )
cm$overall
cm$byClass
```

```{r confusion matrix}
loadPkg("gmodels")
churnPredCross <- CrossTable(cus_test_y, pred, prop.chisq = FALSE)
#Looks like we got all but three correct, not bad
Accuracy = (1505+333)/2349
Precision = 333/535
RecallRate = 333/642 
Specificity = 1505/1507
```
```{r comparing}
# How does the kNN classification compare to the true class?
# Let's take a look at the confusion matrix by combining the 
# predictions from bank_3NN to the original data set.
kNN_res = table(pred,
                cus_test_y)
kNN_res
sum(kNN_res)  #<- the total is all the test examples

# Select the true positives and true negatives by selecting
# only the cells where the row and column names are the same.
kNN_res[row(kNN_res) == col(kNN_res)]

# Calculate the accuracy rate by dividing the correct classifications
# by the total number of classifications.
kNN_acc = sum(kNN_res[row(kNN_res) == col(kNN_res)]) / sum(kNN_res)
kNN_acc
```
```


