---
title: "Telco Customer Churn Project"
author: "Group7-Bug Tornado"
#date: "today"
date: "`r Sys.Date()`"
# this style requires installing rmdformats package 
output:  
    rmdformats::readthedown:
      toc_float: true
      toc_depth: 3
      number_sections: true
      code_folding: hide
      includes:
        before_body: header.html
---

```{r init, include=FALSE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
library(ggplot2)
library(ggpubr)
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```

# Telco Customer Churn
## Description
The Telco customer churn data contains information about a telephone company that provided home phone and Internet services to 7043 customers in California at the end of 2017 Quarter 3. It indicates which customers have left, stayed, or signed up for their service.  
Studying such data can help companies identify the characteristics of lost customers, identify potential, soon-to-be-lost customers and develop appropriate strategies to retain them.  
The dataset is WA_Fn-UseC_-Telco-Customer-Churn.csv.  

### variables

* `gender`: Female or Male
* `SeniorCitizen`: customer is a senior citizen or not (Yes, No)
* `Partner`: customer has a partner or not (Yes, No)
* `Dependents`: customer has dependents or not (Yes, No)
* `tenure`: number of months the customer has stayed with the company
* `PhoneService`: customer has a phone service or not (Yes, No)
* `MultipleLines`: customer has multiple lines or not (Yes, No, No phone service)
* `InternetService`: customer’s internet service provider (DSL, Fiber optic, No)
* `OnlineSecurity`: customer has online security or not (Yes, No, No internet service)
* `OnlineBackup`: customer has online backup or not (Yes, No, No internet service)
* `DeviceProtection`: customer has device protection or not (Yes, No, No internet service)
* `TechSupport`: customer has tech support or not (Yes, No, No internet service)
* `StreamingTV`: customer has streaming TV or not (Yes, No, No internet service)
* `StreamingMovies`: customer has streaming movies or not (Yes, No, No internet service)
* `Contract`: contract term of the customer (Month-to-month, One year, Two year)
* `PaperlessBilling`: customer has paperless billing or not (Yes, No)
* `PaymentMethod`: Electronic check, Mailed check, Bank transfer (automatic), Credit card (automatic)
* `MonthlyCharges`: amount charged monthly
* `TotalCharges`: total amount charged
* `Churn`: customer churned or not (Yes or No)

```{r import, include=FALSE}
customer <- data.frame(read.csv("WA_Fn-UseC_-Telco-Customer-Churn.csv"))
str(customer)
#head(customer)
```

```{r asfactor, include=FALSE}
for(i in 2:21){
  # tenure, MonthlyCharges, TotalCharges
  if (!(i %in% c(6, 19, 20))){
    customer[,i] = factor(customer[,i])
  }
}
levels(customer$SeniorCitizen) <- c("No", "Yes") # no=1, yes=2
str(customer)
```

```{r cleanNA, include=FALSE}
summary(customer)  # there are 11 NA in TotalCharges
customer <- na.omit(customer)
sum(is.na(customer))
```

```{r}
# install.packages(tidyverse)
# install.packages(kernlab)
# install.packages(e1071)
# install.packages(caTools)
library(tidyverse)#SVM
library(kernlab)#SVM
library(e1071)#SVM
library(caTools)#Split Data into Test and Train Set
library(ModelMetrics)#confusion matrix
library(ROCR)#ROC plot
```


```{r}
dat=subset(customer,select=-c(customerID))
set.seed(123)
split <- sample.split(dat, SplitRatio = 0.75)
# split
train_svm <- subset(dat, split == "TRUE")
test_svm <- subset(dat, split == "FALSE")
```


```{r}
# sample training data and fit model
# train <- base::sample(200,100, replace = FALSE)
svmfit <- svm(Churn~., data = train_svm, kernel = "radial", gamma = 1, cost = 1)
# plot classifier
# plot(svmfit, dat)

# Fit radial-based SVM in kernlab
kernfit <- ksvm(subset(train_svm,select=-c(Churn)),train_svm$Churn, type = "C-svc", kernel = 'rbfdot', C = 1, scaled = c())
# Plot training data
# plot(kernfit, data = x[train,])
```

```{r}
# tune model to find optimal cost, gamma values
tune.out <- tune(svm, Churn~., data = train_svm, kernel = "radial",
                 ranges = list(cost = c(0.1,1,10,100,1000),
                 gamma = c(0.5,1,2,3,4)))
# show best model
tune.out$best.model
```

```{r}
print('The parameter of best svm model is:')
tune.out$best.parameters
best_svmfit <- svm(Churn~., data = train_svm, kernel = "radial", gamma = 0.5, cost = 1,probability = TRUE)
```

```{r}
# validate model performance
# valid <- table(true = test_svm$Churn, pred = predict(best_svmfit,test_svm))
# valid
#method 2(confusion matrix)
loadPkg("caret") 
cm = confusionMatrix( predict(best_svmfit,test_svm), reference = test_svm$Churn )
print('Overall: ')
cm$overall
print('Class: ')
cm$byClass
unloadPkg("caret")
```

```{r}
xkabledply(cm$table, "confusion matrix for svm")
```

```{r}

# rocplot(attributes(predict(best_svmfit,test_svm,probability = TRUE))$probabilities[,2], test_svm$Churns, main = "adsfadsfadsfdsf Data")
x.svm.prob <- predict(best_svmfit, type="prob", newdata=test_svm, probability = TRUE)
x.svm.prob.rocr <- prediction(attr(x.svm.prob, "probabilities")[,2], test_svm$Churn)
x.svm.perf <- performance(x.svm.prob.rocr, "tpr","fpr")
plot(x.svm.perf, col=6)

x.glm.prob <- predict(logistic_7, type = "response" )
x.glm.prob.rocr <- prediction(x.glm.prob, customer$Churn)
x.glm.perf <- performance(x.glm.prob.rocr, "tpr","fpr")
plot(x.glm.perf, col=5)

# Draw a legend.
# legend(0.6, 0.6, c('ctree', 'logistic','svm'), 4:6)
```


